A Comparison of Graph Processing Systems

### 2020-09-19 documentation/paper/main.tex
Ideen in Introduction rein gepastet

\section{Introduction}
\todo{Section}
% In recent years graph sizes have increased significantly [?] .
% Thus performance and memory efficiency of the graph analysis applications is now more important than ever.

% Many applications like

% Wachsende graphen,
% benötigt für folgende Applikationen,
% verwenden graph algorithmen,
% diese müssen schnell und verteilt laufen
% dafür wurden Frameworks entwickelt...

% und das noch schön formulieren

% We compare several non-uniform memory access (NUMA) aware systems in terms of their performance on three graph algorithms (PageRank, SSSP, BFS).
% The comparison is performed on both real world data sets and synthetic graphs.

% To provide a comparison to a non-NUMA aware system, Giraph\cite{Giraph} is included in the testing. Giraph itself has often been compared to other state of the art systems like Pregel or GraphX.

%One of the most famous is the (closed source) distributed graph processing system Pregel. Pregel and several open source versions of .
%This results in suboptimal performance, due to missing cache locality, because the Pregel like systems are written in an object oriented manner relying on pointer chasing mechanisms.

% To this end several non-uniform memory access (NUMA) aware systems were proposed like Polymer \cite{Polymer}, Galois \cite{Galois} or Ligra \cite{Ligra}.

This paper makes the following contributions:
\begin{itemize}
  \item Comparison of several state-of-the-art graph processing frameworks
  \item
  \item
  \item
\end{itemize}

@@

>>>>

\input{sections/introduction}

@@

\bibitem{scalability}
\BIBentryALTinterwordspacing
F.~McSherry, M.~Isard, and D.~G. Murray, ``Scalability! but at what {COST}?''
  in \emph{15th Workshop on Hot Topics in Operating Systems (HotOS
  {XV})}.\hskip 1em plus 0.5em minus 0.4em\relax Kartause Ittingen,
  Switzerland: {USENIX} Association, May 2015. [Online]. Available:
  \url{https://www.usenix.org/conference/hotos15/workshop-program/presentation/mcsherry}
\BIBentrySTDinterwordspacing
